### 2017-07-22 introduction.tex
Summary

To address these challenges we introduce two abstractions:
the `safe-collection' to define the scope of a data collection
and the associated policies and the role of a data `steward'
to manage safe collections. These two constructs allow us
to define, manage, and audit access, use, and export of
sensitive data.  We implement these constructs in \NAME and
describe how such implementation enhances security without compromising collaborative agility.

>>>>

To address these challenges we introduce two abstractions:
the `safe collection' to define the scope of a data collection
and the associated policies and the role of a data `steward'
to manage safe collections. These two constructs allow us
to define, manage, and audit access, use, and export of
sensitive data.  We implement these constructs in \NAME and
describe how such implementation enhances security without compromising collaborative agility.
